---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This package holds a single function to calculate and visualize a "songsim" similarity matrix where cell (i, j) is filled if word i in a song's lyrics is the same as word j. This method was first suggested by [Colin Morris](https://colinmorris.github.io/) (see links below).

Install:
```{r, eval = FALSE}
devtools::install_github("gsimchoni/songsim")
```

Load:
```{r}
library(songsim)
```

Visualize Beyonce's Formation:
```{r}
path <- system.file("extdata", "formation.txt", package = "songsim")
songsim(path)
```

Use `colorfulMode`:
```{r}
songsim(path, colorfulMode = TRUE, mainTitle = "Formation - Beyonce")
```

Use `interactiveMode` if you have the `heatmaply` package installed:
```{r, eval = FALSE}
songsim(path, interactiveMode = TRUE, singleColor = "blue")
```
```{r, eval = FALSE}
res <- songsim(path, interactiveMode = TRUE, singleColor = "blue")
hm <- heatmaply::heatmaply(x = res$songMat, dendrogram = FALSE,
                           limits = c(0, 1), showticklabels = FALSE,
                           colors = c("white", "blue"),
                           hide_colorbar = TRUE, plot_method = "plotly")
htmlwidgets::saveWidget(hm, "~/beyonce_formation_hm.html", selfcontained = TRUE)
```

<iframe src="~/beyonce_formation_hm.html" style="position:absolute; height:575px; width:100%"></iframe>
<hr style="height:570px; visibility:hidden;" />

More information and examples [here](http://giorasimchoni.com/2017/08/08/2017-08-08-lambada-the-mocap-package/).

More information from Colin Morris:

* A blog post describing interesting "songsims" [here](https://colinmorris.github.io/blog/weird-pop-songs)

* An interactive React (JS) demo with more examples [here](https://colinmorris.github.io/SongSim/)
